Figures to insert in text

### 2018-04-05 kanerva-answer.tex
SDM Answer to Kanerva.

See Figure \ref{fig:sdm-corr-prob} and notice that I still have to figure out why the mean is correct, but the standard deviation is not. Let $D$ be the number of counters aligned with $\text{addr}_i$. The standard deviation was calculated using the fact that $[D|\theta] \sim \text{Binomial}(1000, P(\text{cnt}_i > 0 | \text{addr}_i=1, \theta))$.

@@

In our case, $\left[ \text{acc}_i|\eta_i=1 \right] \sim \mathcal{N}(\mu = 128.62, \sigma^2 = 12181.95)$, and $\left[ \text{acc}_i|\eta_i=0 \right] \sim \mathcal{N}(\mu = -128.62, \sigma^2 = 12181.95)$. See Figure \ref{fig:sdm-read} --- we can notice that the variance issue from Figure \ref{fig:sdm-read-sums} has propagated to these images.

>>>>

Let $D$ be the number of counters aligned with $\text{addr}_i$. The standard deviation was calculated using the fact that $[D|\theta] \sim \text{Binomial}(1000, q=P(\text{cnt}_i > 0 | \text{addr}_i=1, \theta))$.

Applying the law of total variance, $\mathbf{V}[D] = \mathbf{E}[\mathbf{V}[D|\theta]] + \mathbf{V}[\mathbf{E}[D|\theta]] = \mathbf{E}[1000 q (1-q)] + \mathbf{V}[1000 q] = 1000 \mathbf{E}[q-q^2] + 1000^2 \mathbf{V}[q] = 1000 \mathbf{E}[q](1-\mathbf{E}[q]) + 1000(1000-1)\mathbf{V}[q]$, where $\mathbf{E}[q] = \sum_\theta P(\text{cnt}_i > 0 | \text{addr}_i=1, \theta) P(\theta)$ and $\mathbf{E}[q^2] = \sum_\theta [P(\text{cnt}_i > 0 | \text{addr}_i=1, \theta)]^2 P(\theta)$.

Doing the math, $\mathbf{E}[q] = 0.402922$ and $\mathbf{E}[q^2] = 0.634433$. Thus, $\mathbf{V}[q] = \mathbf{E}[q^2] - (\mathbf{E}[q])^2 = 0.0004166$. Hence, $\mathbf{V}[D] = 648.2041$. See Figure \ref{fig:sdm-corr-prob} and notice that I still have to figure out why the mean is correct, but the standard deviation is not.

@@

In our case, $\left[ \text{acc}_i|\eta_i=1 \right] \sim \mathcal{N}(\mu = 128.62, \sigma^2 = 12865.69)$, and $\left[ \text{acc}_i|\eta_i=0 \right] \sim \mathcal{N}(\mu = -128.62, \sigma^2 = 12865.69)$. See Figure \ref{fig:sdm-read} --- we can notice that the variance issue from Figure \ref{fig:sdm-read-sums} has propagated to these images.
